data_cleaning_longer_period

### 2023-08-25 code/analysis_Redo.Rmd
finalizing contextualizing figures

```{r}
library(readxl)
library(did2s)
library(tidyverse)

@@

@@

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total:Sites) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total:Sites) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

@@

data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.profit[,1]), 
      SD = as.numeric(did.profit[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

@@

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Baseline Profitiability")

@@

data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.size[,1]), 
      SD = as.numeric(did.size[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

@@

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Baseline Size")

@@

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE))%>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid.control = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Patients - Medicaid` = NumberofPatients_Medicaid - NumberofPatients_Medicaid.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 250) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")

>>>>

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
```

@@

##  Trends over time

```{r}
## Plot
p <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>%
  group_by(`BHCMIS ID`, Year) %>%
  summarise(Clinics = max(Clinics, na.rm = TRUE)) %>%
  group_by(Year, Clinics) %>% 
  summarise(Count = n()) %>% 
  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
  group_by(Year, CompetitorsInArea) %>% 
  summarise(Count = sum(Count))

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
  geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 0.75), inherit.aes=T ) + 
  guides(colour = "none") + ylim(0, 4000)

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 0.75), inherit.aes=T ) + 
  guides(colour = "none")

p.desc <- ggarrange(plot1, plot0)

annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))

@@

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total:Sites) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total:Sites) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core, NiceName = c("Total","Quality Composite","Altman's Z","Sites")) %>% 
   select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = NiceName) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

@@

plot.profit <- data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.profit[,1]), 
      SD = as.numeric(did.profit[,2])) %>% 
  #mutate(Subset.f = as.factor(Subset)) %>% 
  mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

@@

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ylab("Stratified by baseline profitability (% of expenses)") + 
  ggtitle("DID Estimates by Baseline Profitiability")

plot.profit
```

@@

data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.size[,1]), 
      SD = as.numeric(did.size[,2])) %>% 
  #mutate(Subset.f = as.factor(Subset)) %>% 
  mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

@@

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ylab("Stratified by baseline clinic population size") + 
  ggtitle("DID Estimates by Baseline Size")

@@

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE))%>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid.control = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Patients - Medicaid` = NumberofPatients_Medicaid - NumberofPatients_Medicaid.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Unadjusted DID Estimates by Distance to Competitive Zip")

### 2023-08-25 code/data_cleaning_longer.Rmd
finalizing contextualizing figures

clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  filter(Year >= included.years[1]) %>% 
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

>>>>

clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>% 
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))
